\documentclass[11pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage{geometry}
\geometry{letterpaper, margin=1in}

\address{Mohammad Havaledar \\ Guelph, ON \\ +1 519 731 8424 \\ \href{mailto:havaledar@gmail.com}{havaledar@gmail.com}}

\begin{document}

\begin{letter}{Operations Manager \\ Core Climbing \\ \href{mailto:ops@thecoreclimbing.ca}{ops@thecoreclimbing.ca}}

    \opening{Dear Operations Manager,}

    I am writing to express my interest in the \textbf{Instructor – Part-Time (Adult Programs Focus)} position at Core Climbing. Building a positive, inclusive community around climbing has been a driving force throughout my career. With extensive experience in climbing instruction, competition officiating, and adult education, I am excited about the opportunity to bring my stoke and knowledge to the adult programs at Core.

    My background closely aligns with the requirements of this role:

    \begin{itemize}
        \item \textbf{Adult Instruction \& Communication:} Drawing on my extensive background as a Climbing Instructor at Payam Climbing Gym, I have organized and delivered engaging instruction to climbers of all ages. As a Graduate Teaching Assistant, I am highly comfortable leading groups, breaking down complex movement techniques into clear lessons, and tailoring my approach to different skill levels.
        \item \textbf{Climbing Movement \& Safety:} Having served as an Event Delegate and Head Judge for Climbing Escalade Canada (CEC), as well as an International Judge for the IFSC and UIAA, safety and risk management are my absolute priorities. I have a deep understanding of climbing movement fundamentals and progression, which I have applied when training athletes, establishing safe sport competition rules, and evaluating climbing courses.
        \item \textbf{Community \& Interpersonal Skills:} Through my roles leading Board initiatives and managing event logistics with the CEC, I have actively collaborated with stakeholders to improve gym environments, promote ethical practices, and create a welcoming atmosphere for both adult and youth climbers. I thrive in team-oriented, collaborative spaces.
    \end{itemize}

    Thank you for considering my application.

    Sincerely, \\ Mohammad Havaledar

\end{letter}

\end{document}
