\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{4.08003pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-4pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge Mohammad Havaledar} \\ \vspace{1pt}
  \small +1 519 731 8424 $|$
  \small \href{mailto:havaledar@gmail.com}{\underline{havaledar@gmail.com}} $|$
  \small Guelph, Ontario
\end{center}

%-----------EXPERIENCE-----------
\section{Climbing Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Iran Mountaineering \& Sport Climbing Federation (IMSCF)}{Tehran, Iran}
{Climbing Instructor, Routesetter \& Judge}{2013 – 2022}
\resumeItemListStart
\resumeItem{Instructed climbing at Payam Climbing Gym for youth and adult climbers, proactively tailoring exercises to varying skill levels.}
\resumeItem{Developed the national Climbing Education System and taught instructing and judging courses, emphasizing a concrete understanding of climbing movement fundamentals and skill progression.}
\resumeItem{Directed youth talent identification camps, leveraging contemporary sports science tools to physically and psychologically evaluate and develop athletes.}
\resumeItemListEnd

\resumeSubheading
{Climbing Escalade Canada (CEC)}{Ottawa, Canada}
{Board of Directors, Event Delegate, Jury President \& Head Judge}{2022 – Present}
\resumeItemListStart
\resumeItem{Officiated at national and regional levels, rigorously enforcing participant safety and risk management protocols.}
\resumeItem{Collaborated effectively with several stakeholders to manage schedules, logistics, and orientations, fostering a highly welcoming environment for both adult and youth events.}
\resumeItem{Led technical evaluations of competitions and persistently updated CEC and North American Cup Series (NACS) competition rules to reflect international best practices.}
\resumeItem{Guided Board of Directors initiatives to promote competition climbing across Canada, driving long-term community value and ensuring ethical, safe operations.}
\resumeItemListEnd

\resumeSubheading
{International Federation of Sport Climbing (IFSC)}{Torino, Italy}
{IFSC Judge}{2015 – Present}
\resumeItemListStart
\resumeItem{Judged at World Cups and Asian Championships, seamlessly evaluating peer judges and demonstrating paramount professionalism towards athletes.}
\resumeItem{Sport Department Member until 2025: Prepared new competition formats and rulesets, continuously promoting safe and high-quality development of the sport on a worldwide scale.}
\resumeItemListEnd

\resumeSubheading
{International Climbing and Mountaineering Federation (UIAA)}{Bern, Switzerland}
{Ice Climbing Commission Member \& International Judge}{2017 – Present}
\resumeItemListStart
\resumeItem{Officiated as Jury President and International Judge across World Championships, World Cups, Youth Championships, and Continental Cups.}
\resumeItem{Managed result services for European Cups and extensively collaborated with the Technical, Rules, Disciplinary, and Speed Development Sub-Commissions.}
\resumeItem{Spearheaded core committee decisions surrounding strategic planning, sustainable development, and global budget formulation.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------
\section{Climbing Publications}
\resumeSubHeadingListStart
\resumeItem{Contributor to \textit{Best Practices} for The Global Climbing Initiative (globalclimbing.org/best-practices).}
\resumeItem{UIAA Ice Climbing Rules.}
\resumeItem{Climbing Escalade Canada (CEC) \& North American Cup Series (NACS) Competition Rules.}
\resumeItem{IMSCF Sport \& Ice Climbing Rules \& Event Organizer Handbook.}
\resumeItem{IMSCF Training Handbooks: Beginner \& Advanced Climbing, Judging, Instructing, and Routesetting.}
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Climbing Certifications \& Safe Sport}
\resumeSubHeadingListStart
\resumeItem{\textbf{Judging:} UIAA International Judge \& Jury President (2017), IFSC Judge Level 1 (2015), IMSCF Ice/Sport Judge (2013/2017), IMSCF Routesetter (2015), IMSCF Climbing Instructor (2013).}
\resumeItem{\textbf{Technical:} FFME (Fédération Française de la Montagne et de l'Escalade) Bolting Certificate (2014).}
\resumeItem{\textbf{Safe Sport:} CAC Safe Sport Training \& Mental Health in Sport Certification, Making Head Way in Sport \& Pre-Season Concussion Protocol Education, NCCP Making Ethical Decisions (MED) Training and Online Evaluation.}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Guelph}{Guelph, ON}
{PhD student in Computational Sciences}{September 2023 – Present}
\resumeItemListStart
\resumeItem{Instructed and organized labs for university students, delivering clear, engaging education with a positive attitude.}
\resumeItem{Mentored students through projects, assisted with curriculum updates, and utilized strong interpersonal and communication skills to foster an inclusive environment.}
\resumeItem{Comfortable leading groups and speaking in front of participants, while working both independently and as part of a team to gather and apply feedback.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}